\documentclass{article}


\title{MP2 Writeup: Level Design \\ \large CS 415}
\author{Benjamin Havens}

\newcommand{\code}{\texttt}

\begin{document}
\maketitle

In order to improve my skills with lighting in Unreal, I opted for a nighttime level. I also added a moon using a texture from NASA, which turned out well and was instructive. After adding an initial island, I added a few cottages for variety. The cottages lining the sides of the island, and framing the moon in the starry sky, inspired the structure of the level.

I envisioned the player spawning in to see the huge moon at the end of a walkway, framed by the cottages, and naturally exploring towards it. At the end, they'd see a rising chain of islands, with the final island silhouetted against the moon, providing a clear purpose for the level. Along the way, each island would provide a new challenge to the player, as well as a path upward to the next island.

For the first island, the mechanics were straightforward: pursuer enemies interrupt the player's attempt to gather points through coins, with the final challenge being to gain enough height to reach the second island. The player cannot move through it too quickly, however, if they want to find the more well hidden coins.

The second island involves the player using the character's flying ability to push up a ramp while collecting coins and features flowers from the starter kit concealing a custom collectible (detailed below). 

The third island features the mortar enemy, with a horde of them providing challenges (and points if killed) while the player collects coins. At the end, the custom enemy is a bouncer. 

Similar to the mortar, the bouncer fires a projectile at the player, but the projectiles do no damage and instead launch the player upwards quickly. It also fires more quickly than the mortar and can aim upward, allowing the player to chain hits from the projectiles to gain height, necessary to reach the final island. I admit it is perhaps a tad similar to the mortar; to make up for this lack of complexity, I also designed: a teleporter pickup that can take the player from a hidden area back to the main map; a speed increase pickup to help the player fly more quickly; and a secret ending to the level that gives a score boost. I also hope the novelty/creativity of the enemy's purpose and the more complex aesthetic of the level balance it out.

The final level features a climb up a mountain (composed of the islands turned over) to the level end\dots\ and also a hidden ledge with a secret. 


	
\end{document}